\documentclass{article}
%\usepackage[utf8]{inputenc}
%\usepackage[russian]{babel}
%\usepackage[active]{srcltx}
\usepackage{amsmath,amssymb} 
\usepackage{titlesec}

\def\noi{\noindent}%  
%\def\ts{\thinspace}%  
\def\CC{\mathbb{C}}%  
\def\PP{\mathbb{P}}%  
\def\NN{\mathbb{N}}%  
\def\RR{\mathbb{R}}%  
\def\ZZ{\mathbb{Z}}% 
\def\QQ{\mathbb{Q}}% 
\def\cC{{\Cal C}}%  
\def\cF{{\Cal F}}%  
\def\cM{{\Cal M}}%  
\def\cS{{\Cal S}}%  
\def\cT{{\Cal T}}%  
\def\eps{\varepsilon}%  
\def\a{\alpha}%  
\def\"#1{{\accent"7F #1\penalty10000\hskip 0pt plus 0pt}} % ! % 

\renewcommand{\theparagraph}{\arabic{paragraph}}
\setcounter{secnumdepth}{4}
\begin{document}
\pagestyle{empty}
\titleformat{\paragraph}[runin]{\normalfont\bfseries}{\theparagraph.}{\wordsep}{}

\section*{Preliminary list of questions for the midterm}

\paragraph{} Inverse function theorem.

%\newpage

\paragraph{} Sard's lemma.

%\newpage

\paragraph{} Degree modulo 2 and integer degree; their homotopy invariance.

%\newpage

\paragraph{} Construction of partition of unity.

%\newpage

\paragraph{} Brouwer fixed-point theorem.

%\newpage

\paragraph{} Thom's traversality theorem, intersection  number.

%\newpage

\paragraph{} Whitney embedding theorem (for closed manifolds).

%\newpage
 
\paragraph{} Vector fields as sections of tangent bundle:
integral curves, flows, straightening lemma.

%\newpage

\paragraph{} Vector fields as a differential operator: Lie bracket, Jacobi identity.

%\newpage

\paragraph{} Straightening lemma for commuting vector fields.

%\newpage

\paragraph{}
Lie derivative of tensor fields: defintions and proof of identities
\[\begin{split}
\mathcal{L}_X(\alpha\otimes\beta)&=(\mathcal{L}_X\alpha)\otimes\beta+\alpha\otimes(\mathcal{L}_X\beta),
\\
\mathcal{L}_{X}\mathrm{Contraction}&=\mathrm{Contraction}\,\mathcal{L}_{X},
\\
\mathcal{L}_{X+Y}&=\mathcal{L}_X+\mathcal{L}_Y,
\\
\mathcal{L}_{X}\mathcal{L}_{Y}-\mathcal{L}_{Y}\mathcal{L}_{X}&=\mathcal{L}_{[X,Y]}.
\end{split}
\]

%\newpage

\paragraph{}
Grassmann algebra and its existence (tensor interpretation).

%\newpage

\paragraph{} Differential forms: definition, Lie, external, and internal derivative,  their product rules, pullback and its relation to wedge product and external differential.

%\newpage

\paragraph{} Cartan's magic formula.

%\newpage

\paragraph{} Stokes' theorem, closed and exact forms.

%\newpage

\paragraph{} De Rham cohomology algebra: definitions, an example of calculations via symmetry.

%\newpage

\paragraph{} Homotopy invariance of De Rham cohomology, Poincaré's lemma.

%\newpage

\paragraph{} Mayer--Vietoris sequence: formulation + an application.

%\newpage

\paragraph{}
Top cohomology.
Cohomological definition of degree.

%\newpage

\paragraph{}
Moser's theorem via Moser's trick.

%\newpage

\paragraph{}
Morse theory:
degenerate and nondegenerate critical points,
existence of Morse function (for closed manifolds),
product structure at noncritical levels.

%\newpage

\paragraph{}
Morse lemma.

%\newpage

\paragraph{} Handle decomposition: rearrangement of handles, handle body decomposition of 3-manifolds (Heegaard splitting).

%\newpage


\end{document}
